RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-03-14 inst/doc/pubs/manuscript.Rmd
writing writing

<!-- Emphasize: 
1) storing character data and tree data together, convenient for the comparative methods community
2) Adding metadata, including automated addition of metadata
3)

@@

* Why RNeXML: Huge ecosystem of phylogenetics packages. (1) Read nexml.
All would benefit by being able to read NeXML, both as a robust standard
free of the pitfalls of Nexus, and more importantly, as a much richer
source of data thanks to its extendable annotation model.  (2) Write
nexml.  R packages and R users add rich information to the phylogenies
they work with, but need a platform independent data exchange format to
share and archive this. (3) Annotate and extend nexml.

* as your own personal treebase

* Adding metadata to capture workflow

>>>>

<!-- Emphasize: 
1) storing character data and tree data together, convenient for the comparative methods community
2) Adding metadata, including automated addition of metadata and semantic utilities 
3) Extending the NeXML standard

@@

* Why RNeXML: Huge ecosystem of phylogenetics packages. (1) Read NeXML.
All would benefit by being able to read NeXML, both as a robust standard
free of the pitfalls of Nexus, and more importantly, as a much richer
source of data thanks to its extendable annotation model.  (2) Write
NeXML.  R packages and R users add rich information to the phylogenies
they work with, but need a platform independent data exchange format to
share and archive this. In particular, we illustrate how NeXML can
be used to distribute both phylogenies and character trait data used in 
many popular phylogenetic comparative methods tools in R.  (3) Annotate 
and extend nexml. `RNeXML` provides convenient tools for adding metadata
to NeXML files, including the automated generation of metadata and examples
of how to extend the NeXML standard to represent new data features without
breaking validation or backwards compatability of the file type.
